The impact of environmental shocks on children's schooling in Bolivia

### 2020-05-07 paper_draft.Rmd
added lagged variables to descriptions

\begin{table}
\centering
\caption{Variable definitions}
\label{variableDefinitions}
\begin{tabular}{ll}
\hline
\hline
Variable name      & Description                                               \\
\hline
Attend          & Binary variable, 1 = attends school                          \\
Register        & Binary variable, 1 = registered for school                   \\
Work reason     & Binary variable, 1 = missing school for work                 \\
Lny             & Log of income per capita (in Bolivianos/month)               \\
Extr            & Binary variable, 1 = below extreme poverty line              \\
Female          & Binary variable, 1 = female                                  \\
Age             & Age in years                                                 \\
Child           & Binary variable, 1 = is child of head of household           \\
Grandchild      & Binary variable, 1 = is grandchild of head of household      \\
Num children    & Number of children in the household                          \\
Secondary       & Binary variable, 1 = in secondary school group               \\
hhhead educ     & Years of education of head of household                      \\
female hhhead   & Binary variable, 1 = female head of household                \\
Floods          & Number of flood occurrences per dept per year                \\
Droughts        & Number of drought occurrences per dept per year              \\
Dept            & Department                                                   \\
Valleys         & Binary variable, 1 = department is in valleys region         \\
Mountains       & Binary variable, 1 = department is in mountains region       \\
Plains          & Binary variable, 1 = department is in plains region          \\

@@

summary_total <- reg_data %>%
  select(attend, register, work_reason, lny, extr, female, age, child, grandchild, num_children, secondary, hhhead_educ, female_hhhead, floods, droughts, dept, valleys, plains, mountains)%>%
    summarise_all(list(mean = mean, sd = sd))

stargazer::stargazer(as.data.frame(summary_total), 
                     summary = T,
                     label = "summaryStats",
                     title = "Summary statistics (full sample)",
                     header = F,
                     type = "latex",
                     digits = 3)

#creating a table dividing the characteristics by urban/rural area
summary_rural <- rural %>%
  select(attend, register, work_reason, lny, extr, female, age, child, grandchild, num_children, secondary, hhhead_educ, female_hhhead, floods, droughts, dept, valleys, plains, mountains) %>%
    summarise_all(list(mean = mean, sd = sd))

stargazer::stargazer(as.data.frame(summary_rural),
                     label = "summaryStatsR",
                     title = "Summary statistics (rural sample)",
                     summary = T,
                     header = F,
                     type = "latex",
                     digits = 3)

>>>>

\begin{table}
\centering
\caption{Variable definitions}
\label{variableDefinitions}
\begin{tabular}{ll}
\hline
\hline
Variable name      & Description                                               \\
\hline
Attend          & Binary variable, 1 = attends school                          \\
Register        & Binary variable, 1 = registered for school                   \\
Work reason     & Binary variable, 1 = missing school for work                 \\
Lny             & Log of income per capita (in Bolivianos/month)               \\
Extr            & Binary variable, 1 = below extreme poverty line              \\
Female          & Binary variable, 1 = female                                  \\
Age             & Age in years                                                 \\
Child           & Binary variable, 1 = is child of head of household           \\
Grandchild      & Binary variable, 1 = is grandchild of head of household      \\
Num children    & Number of children in the household                          \\
Secondary       & Binary variable, 1 = in secondary school group               \\
hhhead educ     & Years of education of head of household                      \\
female hhhead   & Binary variable, 1 = female head of household                \\
Floods          & Number of flood occurrences per dept per year                \\
Droughts        & Number of drought occurrences per dept in current year       \\
Lag floods      & Number of flood occurrences per dept in the previous year    \\
Lag droughts    & Number of drought occurrences per dept in the previous year  \\
Dept            & Department (nine options)                                    \\
Valleys         & Binary variable, 1 = department is in valleys region         \\
Mountains       & Binary variable, 1 = department is in mountains region       \\
Plains          & Binary variable, 1 = department is in plains region          \\

@@

table_total <- reg_data %>%
  select(attend, register, work_reason, lny, extr, female, age, child, grandchild, num_children, secondary, hhhead_educ, female_hhhead, floods, droughts, dept, valleys, plains, mountains)

stargazer::stargazer(as.data.frame(table_total), 
                     summary = T,
                     label = "summaryStats",
                     title = "Summary statistics (full sample)",
                     header = F,
                     type = "latex",
                     digits = 3)

#creating a table dividing the characteristics by urban/rural area
table_rural <- rural %>%
  select(attend, register, work_reason, lny, extr, female, age, child, grandchild, num_children, secondary, hhhead_educ, female_hhhead, floods, droughts, dept, valleys, plains, mountains)

stargazer::stargazer(as.data.frame(table_rural),
                     label = "summaryStatsR",
                     title = "Summary statistics (rural sample)",
                     summary = T,
                     header = F,
                     type = "latex",
                     digits = 3)
